---
title: "index"
output: html_document
---

```{r, echo=FALSE,  message=FALSE, warning=FALSE}
library(dplyr)
library(plotly)

# Read in the data and rename the columns
data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-collaborative-coding/master/data/intro_survey_data.csv?token=AP1NbC6w-vFziH4uo-eMA9wqFp2X73pjks5W1Mc8wA%3D%3D  ")
names(data)[names(data)=="What.is.your.current.class.standing."] <- "class_standing"
names(data)[names(data)=="Are.you.interested.in.applying.to.the.Informatics.major."] <- "info_interest"
names(data)[names(data)=="What.operating.system.do.you.typically.use."] <- "operating_system"
names(data)[names(data)=="Using.the.command.line...terminal"] <- "command_line_terminal"
names(data)[names(data)=="What.is.your.familiarity.with..using.git.for.version.control"] <- "familiarity_git_for_vc"
names(data)[names(data)=="What.is.your.familiarity.with..Creating.documents.with.Markdown"] <- "familiarity_md"
names(data)[names(data)=="What.is.your.familiarity.with..Using.the.R.programming.language"] <- "familiarity_r"
names(data)[names(data)=="What.is.your.programming.experience."] <- "programming_exp"
names(data)[names(data)=="How.many.countries.have.you.visited.in.your.life."] <- "countries_visited"
names(data)[names(data)=="Do.you.consider.yourself."] <- "dog_or_cat_person"
names(data)[names(data)=="Are.you.a.Seahawks.fan."] <- "go_hawks"

# Source the three functions from their files
source('scripts/summary.r')
source('scripts/chart1.r')
source('scripts/chart2.r')

# Assign list collected from summary
summary_data <- as.data.frame(summary(data))

```

## Summary
The class breakdown from the survey was `r summary_data$freshmen` Freshmen, `r summary_data$sophomore` Sophomores, `r summary_data$junior` Juniors, and `r summary_data$senior` Seniors. `r summary_data$info_interest` of `r summary_data$participants` participants indicated that they are interested in applying for the Informatics major. `r summary_data$windows` responded that they use Windows operating systems, while `r summary_data$mac` responded that they use a Mac OS. The average number of countries respondents have visited is `r round(summary_data$ave_countries_visited,3)`. `r summary_data$hawks_fans` of us are Seahawks fans.

## Chart One
```{r , echo=FALSE}
chart_one(data)
```

## Chart Two
```{r , echo=FALSE}
chart_two(data)
```